### 2019-05-14 doc/chapters/introduction.tex
fixed some typos
Updated fromal verificaiton vs. testing in introduction.tex

In this work some experiments in formal verification of Scala code will be accomplished. 
The framework Stainless is used as a verification tool. The code of Bitcoin-S, Scala implementation of Bintcoin, is taken as an input for Stainless to be verified. 
In following the main aspects of formal verification, Stainless and Bitcoin-S are described.

@@

\section{Formal verification (formal verification vs. simulation-based)}
\label{sec:formal_verification}

The longer and complexer a source code is, the more difficult it is to verify its correctness.
There are two main approaches for verification of program correctness.

The commonly used one is the simulation-based verification.
To simulate a software design a set of some practical scenarios and assertions is created by a developer at the software testing stage. 
While testing it is tried to identify a design error by generating an input which can activate a bug.
It is not achievable to simulate all possible states and to test all possible inputs. 
Thus, a long-term test coverage model should be created to simulate a software design enough.
Furthermore it is challenging to test a software keeping the ability to observe the side effects of a specific part of code.
Practically, a developer runs tests, debugs appeared failures, adjustes a code of a software and extands a testbench verifying previously uncovered aspects. \cite{sanghavi:formal_verification}

Another powerfull method to discover whether a program works correct is formal verification. 
This is a systematic process based on mathematical modeling. 
It is unnecessary to create a simulation tests with some possible inputs. 
With formal verification all possible input values are explored algorithmically and exhaustively.
Correctness of a program is analyzed relative to its formal specification.
Formal specification is a mathematical description of a software behavior that can be provided to formal verification tools for proving it. \cite{sanghavi:formal_verification}

One of such tools is Stainless. It is used in this work to verify a Scala code.

>>>>

In this work some experiments in formal verification of Scala code will be accomplished. 
The framework Stainless is used as a verification tool. The code of Bitcoin-S-Core, Scala implementation of Bitcoin protocol, is taken as an input for Stainless to be verified. 
In following the main aspects of formal verification, Stainless and Bitcoin-S are described.

@@

\section{Formal verification (formal verification vs. testing)}
\label{sec:formal_verification}

The longer and complexer a source code is, the more difficult it is to verify its correctness.
There are different approaches for verification of program correctness.

The commonly used one is testing. A set of some practical scenarios and assertions is created by a developer to test a software design and implementation. 
While testing it is checked whether the actual results match the expected results. Tests help to identify bugs and missing requirements.
But it is not achievable to test all possible inputs. 
Thus, a long-term test coverage model should be created to test a software design enough.
Furthermore it is challenging to test a software keeping the ability to observe the side effects of a specific part of code.
Practically, a developer runs tests, debugs appeared failures, adjustes a code of a software and extands a testbench verifying previously uncovered aspects. \cite{sanghavi:formal_verification}

Another powerfull method to check whether a program works correct is formal verification. 
This is a systematic process based on mathematical modeling. 
It is unnecessary to create a simulation tests with some possible inputs. 
With formal verification all possible input values are explored algorithmically and exhaustively.
Correctness of a program is analyzed relative to its formal specification.
Formal specification is a mathematical description of a software behavior that can be provided to formal verification tools for proving it. \cite{sanghavi:formal_verification}

One of such tools is Stainless. This framework is used in the work to verify a Scala code.
